Data Preparation, Integration and Cleaning

### 2018-05-22 scripts/3_data_prep.Rmd
Begin conversion of paper

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, file=paste0(data_path, '/prepared/prepared_data.RData'))

>>>>

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_count,
        file=paste0(data_path, '/prepared/prepared_data.RData'))
